---
title: "R Project 1 - Hello R"
author: "Keoshia Grigsby"
date: "02/02/2021"
output:
  html_document: 
    fig_width: 10
    fig_height: 10
    fig_caption: yes
    highlight: pygments
    theme: journal
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)

```


### Exercise 1

1. 1846 rows and 3 variables
2. the variables included are x, y, and dateset


### Exercise 2


First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

First let's plot the data in the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))

```
How does this value compare to the r of dino? 
  The r for dino and circle are close
  
  
### Exercise 5
All Datasets:
``` {r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in   3 cols
  theme(legend.position = "none")
```

Dataset correlation between `x` and `y`:
```{r}

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)

```
